An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-05 jmiv.tex
Fix wrong parameter value in plot
Further clarification of inversing the solution in section 4

Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$. In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$. We also use the notation $| S |$ to denote the cardinal of a digital set $S$.

@@

We start by definition the optimization variables.
\begin{definition}[Inner pixel boundary]
Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $I(S)$ as
\begin{align*}
	I(S) = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
\end{align*}
where $\mathcal{N}_4(p)$ denotes the $4$-adjacent neighbor set of $p$ (without $p$).
\end{definition}

@@

Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.

@@

		\setcounter{subfigure}{-2}
		\subfloat[$r=5,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r5-h0.5/summary_flow.eps}
		}%1
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r5-h0.5/summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
		}\\
		\subfloat[Elastica evaluation]{%
		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}						
		}
\caption{The choice of radius impacts the flow. In the figures, the flow ceases to evolve for all shapes  when $r=3$ (a). In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a). In figure (c), we observe that for a given choice of radius, the elastica may increase after a certain number of iterations. }
\label{fig:mx-flow-gs-radius-effect}
\end{figure}

>>>>

Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.

We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Enforcing this restriction implies to incorporate topological information in the form of constraints or penalization terms in the same lines of \cite{schoenemann09linear}, but such approach would result in a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to create a flow that evolves proportionally to the squared curvature of the current shape.

 In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$. We also use the notation $| S |$ to denote the cardinal of a digital set $S$.

@@

We start by defining the optimization variables.
\begin{definition}[Inner pixel boundary]
Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $I(S)$ as
\begin{align*}
	I(S) = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
\end{align*}
where $\mathcal{N}_4(p)$ denotes the $4$-adjacent neighbor set of $p$ (without $p$).
\end{definition}

@@

We remark that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model. Instead, the minimization of \eqref{eq:energy-family} is used as a guide. Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.

@@

		\setcounter{subfigure}{-2}
		\subfloat[$r=5,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r5-h0.5/summary_flow.eps}
		}%1
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r5-h0.5/summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
		}\\
		\subfloat[Elastica evaluation]{%
		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
		}
\caption{The choice of radius impacts the flow. In the figures, the flow ceases to evolve for all shapes  when $r=3$ (a). In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a). In figure (c), we observe that for a given choice of radius, the elastica may increase after a certain number of iterations. }
\label{fig:mx-flow-gs-radius-effect}
\end{figure}
